### 2024-08-27 parts/correction.tex
polish

\begin{corollary}
	\label{decide-rat-poly-npoly:cor}
	Let $P \in \Rat[\vec{X}]$ be a polynomial with \emph{rational}
	coefficients and let $\alpha$ be the smallest number in $\Nat_{\geq 1}$
	such that $\alpha P \in \Rel[\vec{X}]$. Then, there exists a
	computable $K \in \Nat$, such that the following are equivalent:
	\begin{enumerate}
		\item \label{rat-npoly-1:item}
		      $P$ is a \kl{strongly natural binomial polynomial} \kl{in base $K$},
		\item \label{rat-npoly-2:item} $P$ is \kl{represented} by a \kl{$\Nat$-polyregular function},
		\item \label{rat-npoly-3:item} $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
		\item \label{rat-npoly-4:item} $\alpha P \in \CorrectPoly$,
		      and for all $\vec{x} \in \Nat^{\vec{X}}$,
		      $P(\vec{x})$ is a multiple of $\alpha$.
	\end{enumerate}
	In particular, the properties are decidable.
\end{corollary}
\begin{proof}
	First, \cref{rat-npoly-4:item} $\implies$ \cref{rat-npoly-3:item}, because
	if $\alpha P \in \CorrectPoly$, then it is an \kl{$\Nat$-rational
		polynomial}. But in particular, there exists a polyregular function $f$
	that represents $\alpha P$ with outputs in $\set{ a }$. Now, let us
	post-compose this function by the one that maps $a^{k \alpha + r}$ to
	$a^{k}$, which is a \kl{polyregular function}. We conclude that $P$ is
	\kl{represented} by an \kl{$\Nat$-polyregular function}.

	We also know that \cref{rat-npoly-2:item} $\implies$
	\cref{rat-npoly-4:item}, since if $P$ is an \kl{$\Nat$-rational
		polynomial}, then so is $\alpha P$, and in particular $\alpha P \in
		\CorrectPoly$ by \cref{corrected-version:thm}.
\end{proof}

>>>>

\begin{corollary}
	\label{decide-rat-poly-npoly:cor}
	Let $P \in \Rat[\vec{X}]$ be a polynomial with \emph{rational}
	coefficients and let $\alpha$ be the smallest number in $\Nat_{\geq 1}$
	such that $\alpha P \in \Rel[\vec{X}]$. Then, there exists a
	computable $K \in \Nat$, such that the following are equivalent:
	\begin{enumerate}
		\item \label{rat-npoly-1:item} $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
		\item \label{rat-npoly-2:item}
		      $P$ is a \kl{strongly natural binomial polynomial} \kl{in base $K$},
		\item \label{rat-npoly-3:item} $P$ is \kl{represented} by a \kl{$\Nat$-polyregular function},
		\item \label{rat-npoly-4:item} $\alpha P \in \CorrectPoly$,
		      and $P(\Nat^k) \subseteq \Nat$.
	\end{enumerate}
	In particular, the properties are decidable.
\end{corollary}
\begin{proof}
	First, \cref{rat-npoly-4:item} $\implies$ \cref{rat-npoly-3:item}, because
	if $\alpha P \in \CorrectPoly$, then it is an \kl{$\Nat$-rational
		polynomial}. But in particular, there exists a polyregular function $f$
	that represents $\alpha P$ with outputs in $\set{ a }$.
	Now, let us
	post-compose this function by the one that maps $a^{k \alpha + r}$ to
	$a^{k}$, which is a \kl{polyregular function} (but is not
	a \kl{star-free polyregular function}). We conclude that $P$ is
	\kl{represented} by an \kl{$\Nat$-polyregular function}.

	Let us now prove by induction on the number of indeterminates that
	\cref{rat-npoly-2:item} $\implies$
	\cref{rat-npoly-1:item}. When the input values of $P$ are all
	greater than $K$, $P$ coincides with a \kl{natural binomial function},
	which is \kl{represented} by a \kl{star-free $\Nat$-polyregular function}. If some
	input value $X_i$ is set to a number $x_i \leq K$, then one can leverage
	the fact that $\restr{P}{X_i = x_i}$ remains a \kl{strongly natural
		binomial polynomial} \kl{in base $K$}, and we conclude by induction that
	$\restr{P}{X_i = x_i}$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular
		function}. Combining these functions, we obtain a \kl{star-free $\Nat$-polyregular
		function} \kl{representing} $P$.

	Finally, \cref{rat-npoly-1:item} $\implies$
	\cref{rat-npoly-4:item} is obtained via
	\cref{corrected-version:thm} by
	remarking that the
	\kl{star-free $\Nat$-polyregular functions} have output in $\Nat$ and are
	closed under multiplication by a constant $\alpha \in \Nat$.

	To conclude, it remains to show that
	\cref{rat-npoly-3:item} $\implies$ \cref{rat-npoly-2:item}.
\end{proof}
